\subsection{CAPTCHA rating parameters}
CAPTCHA systems use a variety of methods in their decision process. Every method
has its own strengths and limitations, but the following parameters have been
chosen to uniformly rate CAPTCHA methods and systems in an attempt to compare
them.

\begin{description}[\IEEEsetlabelwidth{Effectiveness}]
\item[Privacy] 
	\begin{itemize}
		\item Does the method use trackers or any other identifying method?
		\item Does the method work in anonymous networks like TOR?\
	\end{itemize}
\item[Effectiveness]
	\begin{itemize}
		\item Is the method/system effective in containing DoS attacks? 
		\item Can the method be circumvented? If yes, how practical or feasible
			is the attack? If the method has feasible or practical
			circumventions, it is immediately marked `bad' for effectiveness.
	\end{itemize}
\item[Accessibility]
	\begin{itemize}
		\item Is the method posing any challenges to visually to users
			with auditory, cognitive and visual disabilities? 
		\item How easy is it to use?
		\item Does the method have a language dependency which poses a challenge to
		non-English speakers?
	\end{itemize}
	If a method is impossible to use for any group of users, some of which are
	mentioned above, 
\item[Accuracy]
	\begin{itemize}
		\item How accurate is the method in detecting potentially malicious
			users?
		\item Are there any factors that method's impact accuracy?
	\end{itemize}
	Bad accuracy when circumventions are used results downgrades `good' to `bad'
	rating.
\end{description}
